Fifteen years of decentralization attempts

### 2014-03-24 paper.tex

			The directory service generates overhead on the network. Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance. Furthermore, it would alleviate a security concern. A malicious adversary could gain control of the directory server and force a connection through a set of colluding nodes. In a decentralized environment such an attack would be much more difficult. In conclusion, this means that we would like to see Tor decentralized. Although much research has been done on the decentralization of Tor, it still uses centralized components today.
		\end{itemize}

		\subsection{Tor stinks}
			The anonymous communication with Tor can also be used for distribution illegal content or setting up illegal services. Illegal content and services are a serious problem that Tor is facing. A recent example is the shutdown of \emph{Silk Road}, an online market for trading drugs. This market operated as a hidden Tor service. These hidden services are accessed through their onion address and not through their IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.

>>>>

		\end{itemize}

		The directory service generates overhead on the network. Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance. In conclusion, this means that we would like to see Tor decentralized. Although much research has been done on the decentralization of Tor, it still uses centralized components today.

		\subsection{Tor stinks}
			Because communication over Tor is untraceable, it is used as a tool for distributors of illegal content and providers of illegal services. This is a serious problem that is disrupting Tor's public image. A recent example is the shutdown of \emph{Silk Road}, which is an online market for trading prohibited substances. The market operated as a hidden Tor service. These services are accessed through an onion address and not an IP-address, hiding the physical location of the service. This makes it very hard for agencies to track and shut down these operations.
